---
title: "Survey: Light logger form factor and placement"
authors: "Johannes Zauner, Anna Biller, Manuel Spitschan"
format: 
  html:
    code-fold: true
    embed-resources: true
    code-tools: true
    toc: true
---

## Preface

This is the analysis for an online survey to gather information about the acceptability of form factor and placements of light loggers. The survey was conducted using Prolific on three days in 2023, each collecting from a different sample (USA, UK, Worldwide).

**This is the second part of the analysis, focusing on inference.**

## Import

We will start off by importing the data and setting factor levels.

```{r, import}
#| output: false

#Load Hmisc library
library(Hmisc)
library(tidyverse)
library(gtsummary)
library(gt)
library(ggtext)
library(rlang)
library(patchwork)
library(ordinal)
library(rlang)
library(glue)
library(broom)
library(ggridges)

#Read Data in the long format
load(file = "data/cleaned/LightLoggerFormFacto_Long_CLEANED_DATA_2024-07-02.RData")
```

## Inferential statistics

The base hypothesis is that the ratings depend on the `Wearing Position`, with `Sex` and `Sample` as control variables. Further, the effect of the `Wearing Position` might be dependent on `Sex`.

The inferential analysis fits cumulative link mixed models (CLMM) to the data. The models are fitted using the `ordinal` package. The models are fitted for each rating separately. The base model is fitted with the following formula:

`CLMM`: $E(logit(y)) = \alpha_0 + \beta_{i1} * WearingPosition + \beta_{i2} * Sex + \beta_{i3} * WearingPosition*Sex + \beta_{i4} * Sample + \alpha_j$

Where $E(logit(y))$ is the expected value of the rating on a logit scale, $\alpha_0$ is the intercept, $\beta_{i1}$ is the effect size of `Wearing Position`, $\beta_{i2}$ is the effect size of `Sex`, $\beta_{i3}$ is the interaction effect size of `Wearing Position` and `Sex`, $\beta_{i4}$ is the effect size of `Sample`, and $\alpha_j$ is the random intercept for each participant.

or in Wilkinson notation:

$Rating \sim WearingPosition*Sex + Sample + (1|Id)$ (m1)

Models are compared through likelihood ratio tests. The following models are used for comparison:

A model without the interaction of `Wearing Position` and `Sex` (m2), a model without `Sex` (m3), a model without `Sample` (m4), a model with only `Wearing Position` (m5), and a null model, with only random effects (m0).

-   $Rating \sim WearingPosition + Sex + Sample + (1|Id)$ (m2)

-   $Rating \sim WearingPosition + Sample + (1|Id)$ (m3)

-   $Rating \sim WearingPosition*Sex + (1|Id)$ (m4)

-   $Rating \sim WearingPosition + (1|Id)$ (m5)

-   $Rating \sim 1 + (1|Id)$ (m0)

The following comparisons are made: 1. Interaction of `Sex` and `Wearing Position` (m1 vs. m2) 2. Inclusion of `Sex` (m2 vs. m3) 3. Inclusion of `Sample` (m1 vs. m4) 4. Inclusion of `Wearing Position` (m5 vs. m0)

The p-values are adjusted using the Benjamini & Hochberg (1995) method, also called the false discovery rate (fdr) with an `n=4` for four comparisons.

### Setup

```{r, general setup}
#convert some variables to factor
data_long$sample_location <- as.factor(data_long$sample_location)
data_long$record_id <- as.factor(data_long$record_id)

#function generation
Infe <- function(parameter, data) {
  parameter <- enexpr(parameter)
  
  #formula generation
  formulas <- inject(c(
    #full formula
    m1 = !!parameter ~ wearing_position*demographics_sex + sample_location + (1|record_id),
    #excluding interaction from m1
    m2 = !!parameter ~ wearing_position + demographics_sex + sample_location + (1|record_id),
    #further excluding sex from m2
    m3 = !!parameter ~ wearing_position + sample_location + (1|record_id),
    #excluding sample location from m1
    m4 = !!parameter ~ wearing_position*demographics_sex + (1|record_id),
    #excluding sample location from m3
    m5 = !!parameter ~ wearing_position + (1|record_id),
    #Null model
    m0 = !!parameter ~ 1 + (1|record_id)
  ))
  
  #Model generation
  Infe_table <- tibble(
    name = names(formulas),
    formula = formulas,
    model = map(name, \(x) {switch(x,
                                        m1 = ,
                                        m2 = ,
                                        m3 = ,
                                        m4 =
                                         clmm(formulas[[x]], data = data, nAGQ = 10,
                                              subset =
                                                demographics_sex != "Other"),
                                        m5 = ,
                                        m0 = clmm(formulas[[x]], data = data, nAGQ = 10)
                                       ) 
    }
    )
  )
  
  Infe_table
}

# Function to perform anova on model pairs
anova_models <- function(pair) {
  one <- pair[[1]]
  two <- pair[[2]]
  inject(anova(Models$model[[!!one]], Models$model[[!!two]]))
}

#function to perform the model comparisons
Model_Comparisons <- function(Models) {
  # Define the model comparisons
model_comparisons <- list(
  c(1, 2),
  c(2, 3),
  c(1, 4),
  c(5, 6)
)

tibble(
  desc = c("interaction of sex and wearing position",
           "inclusion of sex",
           "inclusion of sample location",
           "inclusion of wearing position"),
  p.value = map(model_comparisons, 
                   \(x) anova_models(x) %>% .$`Pr(>Chisq)` %>% .[[2]]
                   ) %>% unlist() %>% p.adjust(method = "fdr", n = 4) %>% 
                    {case_when(
                     . < 0.001 ~ "<0.001",
                     TRUE ~ as.character(round(., 3))
                   )}
    
)
}

#probability of different answers
#setting up a function
pred <- function(eta, theta, levels, cat = 1:(length(theta)+1), inv.link = plogis) {
   Theta <- c(-Inf, theta, Inf)
   eta <- c(reference = 0, eta)
   table <- 
   sapply(cat, function(j)
          inv.link(Theta[j+1] - eta) - inv.link(Theta[j] - eta) ) 
   colnames(table) <- levels
   table
}

data_significance_matrix <- function(Model, subset = "none") {
  Models <- tibble(
  reference = levels(data_long$wearing_position),
  data = map(reference, 
             \(x) data_long %>% mutate(wearing_position = 
                                         fct_relevel(wearing_position, x))
             ),
  model = map(data, 
              \(x) switch(subset,
                          none = clmm(Model$formula, data = x, nAGQ = 10),
                          clmm(Model$formula, data = x, nAGQ = 10,
                               subset = demographics_sex != "Other")
                          )
              ),
  tidy = map(model, 
             \(x) tidy(x) %>% 
               filter(str_detect(term, "wearing_position")) %>% 
               select(term, p.value) %>% 
               mutate(term = str_remove(term, "wearing_position"))
             )
  )

Models %>% 
  select(-data, -model) %>% 
  unnest(tidy) %>% 
  rowwise() %>% 
  mutate(
    p.value = p.adjust(p.value, method = "fdr", n = 7),
    different = p.value <= 0.05) %>%
  ungroup() %>% 
  rbind(
    tibble(reference = levels(data_long$wearing_position),
           term = reference,
           p.value = NA,
           different = FALSE))
}

#McFadden´s Pseudo R2, values between 0.2 bis 0.4 are an excellent model fit
McFadden <- function(model, nullmodel) {
  ll.null <- nullmodel$logLik
  ll.proposed <- model$logLik
  1 - ll.proposed/ll.null
}

#Formula to plot the significance matrix
Significance_matrix <- function(sig_matrix, sex = FALSE){
  sig_matrix %>% 
  mutate(
    across(c(reference, term), \(x) fct_relevel(x, levels(data_long$wearing_position)))) %>%
  ggplot(aes(x=reference, y = term, fill = different)) +
  geom_tile(col = "grey30") + 
  scale_fill_manual(values = c("white", "skyblue4"))+
  coord_fixed() +
  theme_void() +
  labs(title = label(data_long[parameter]),
       subtitle = case_when(!sex ~ "<span style='color:skyblue4'>Significant differences</span> due to wearing position",
                            sex ~ "Significant differences due to <span style='color:skyblue4'>wearing position</span> and <span style='color:red'>sex</span>" )
       )+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.text.y = element_text(hjust = 1),
        plot.title = 
          element_textbox_simple(
            hjust = 0,
            padding = margin(0.5, 0, 0.5, 0, "cm")),
        plot.subtitle = element_textbox_simple(),
        plot.title.position = "plot",
        )
}

#table of probabilities
prob_table <- function(beta, title){
pred(beta, Model$Theta, 
     levels = levels(data_long[[parameter]])) %>% 
  as_tibble(rownames = "Wearing Position") %>%
  mutate(`Wearing Position` = 
           str_remove(`Wearing Position`, "wearing_position"),
         `Wearing Position` = str_replace(`Wearing Position`, "reference", "Chest Pin")
           ) %>%
  gt() %>% fmt_percent() %>% 
  gt::tab_caption(md(glue(title)))
}

```

::: panel-tabset
### Appearance

#### Model selection

```{r, appearance model selection}
parameter <- "appearance"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The only parameter which is supported by the data is `Wearing Position`. `Sex`, its interaction with `Wearing Position`, and `Sample` are not supported by the data. The resulting model `m5` is used for the following analysis.

#### Significant differences

```{r appearance differences}
#final model
chosen_model <- "m5"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])



#Significance matrix
sig_matrix <- data_significance_matrix(Model)

P1 <- Significance_matrix(sig_matrix)

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P1, width = 4, height = 4.6)

P1

```

#### Predicted probabilities

```{r appearance predictions}
#if one wanted to print predictions for different subject percentiles
stDev <-  as.numeric(attr(VarCorr(Model)$record_id, "stddev"))^2
# 5th percentile:
prob_table(Model$beta * qnorm(0.05) * stDev, 
           "Predicted probabilities for the **5th percentile** for **{parameter}**")
#average:
prob_table(Model$beta, 
           "Predicted probabilities for the **average person** for **{parameter}**")
# 95th percentile:
prob_table(Model$beta * qnorm(0.95) * stDev, 
           "Predicted probabilities for the **95th percentile** for **{parameter}**")

```

#### Model diagnostics

```{r, appearance diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
for(i in 1:145) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Wearlikelihood context

This sections analyses how the context of wear influences the ratings, dependent on the wearing position

```{r, wearlikelihood context}
#function to remove labels. This is necessary for pivot_longer to work
clear.labels <- function(x) {
  if(is.list(x)) {
    for(i in seq_along(x)) {
      class(x[[i]]) <- setdiff(class(x[[i]]), 'labelled') 
      attr(x[[i]],"label") <- NULL
    } 
  } else {
    class(x) <- setdiff(class(x), "labelled")
    attr(x, "label") <- NULL
  }
  return(x)
}

#pivoting the data even longer to get the context into the observation
data_long2 <- data_long %>% 
  select(record_id,
         demographics_sex,
         wearing_position,
         starts_with("wearlikelihoodrating")
  ) %>% 
  clear.labels() %>% 
  pivot_longer(-c(record_id, demographics_sex, wearing_position), 
               names_to = "context", 
               values_to = "rating") %>% 
  mutate(context = 
           str_remove(context, "wearlikelihoodrating_") %>% 
           factor() %>% 
           fct_reorder(as.numeric(rating), .desc = TRUE, .fun = mean)
           # fct_relevel(c("public", "work", "home", "social", "exercise")
           )

#model generation
Model <- clmm(rating ~ context*wearing_position + (1|record_id), data = data_long2, nAGQ = 10)
Model2 <- clmm(rating ~ context+wearing_position + (1|record_id), data = data_long2, nAGQ = 10)
Model3 <- clmm(rating ~ context + (1|record_id), data = data_long2, nAGQ = 10)
Model4 <- clmm(rating ~ wearing_position + (1|record_id), data = data_long2, nAGQ = 10)
Model0 <- clmm(rating ~ 1 + (1|record_id), data = data_long2, nAGQ = 10)

#model selection
anova(Model, Model2)
anova(Model2, Model3)
anova(Model3, Model0)
anova(Model4, Model0)

#model summaries
summary(Model)
summary(Model3)
summary(Model4)

#get the predicted probabilities depending on context, save as a table
context_preds <- pred(Model3$beta, Model3$Theta, 
     levels = levels(data_long2$rating)) %>% 
  as_tibble(rownames = "Parameters") %>%
  mutate(`Parameters` = 
           str_remove(`Parameters`, "wearing_position|context"),
         `Parameters` = str_replace(`Parameters`, "reference", "home")
           )

context_preds_table <- 
context_preds %>% 
  gt() %>% 
  fmt_percent(decimals = 0) %>% 
  gt::tab_caption(md("Likelihood of wear ratings depending on context")) %>% 
  gt::data_color(columns = -Parameters, method = "numeric", 
                 colors = scales::col_numeric(palette = "viridis", 
                                              domain = c(0,0.30))
                 ) %>% 
  cols_width(everything() ~ px(100))

context_preds_table
gtsave(context_preds_table, "output/02_tables/table_2_context.png")

#get the predicted probabilities depending on wearing_position, save as a table
context_preds <- pred(Model4$beta, Model4$Theta, 
     levels = levels(data_long2$rating)) %>% 
  as_tibble(rownames = "Parameters") %>%
  mutate(`Parameters` = 
           str_remove(`Parameters`, "wearing_position|context"),
         `Parameters` = str_replace(`Parameters`, "reference", "Chest pin")
           )

context_preds_table <- 
context_preds %>% 
  gt() %>% 
  fmt_percent(decimals = 0) %>% 
  gt::tab_caption(md("Likelihood of wear ratings depending on wearing position")) %>% 
  gt::data_color(columns = -Parameters, method = "numeric", 
                 colors = scales::col_numeric(palette = "viridis", 
                                              domain = c(0,0.39))
                 ) %>% 
  cols_width(everything() ~ px(100))

context_preds_table
gtsave(context_preds_table, "output/02_tables/table_3_wearing_position.png")

#create a table of the interaction model
#first, collect all the beta coefficients for the context
coefs_context <- 
  Model$beta %>% 
  as_tibble(rownames = "Parameters") %>% 
  filter(str_detect(Parameters, "context"),
         !str_detect(Parameters, "wearing_position")) %>% 
  rename(Context = Parameters,
         beta1 = value) %>% 
  add_row(Context = "contexthome", beta1 = 0, .before = 1)

#second, collect all the beta coefficients for the wearing position
coefs_position <- 
  Model$beta %>% 
  as_tibble(rownames = "Parameters") %>% 
  filter(str_detect(Parameters, "wearing_position"),
         !str_detect(Parameters, "context")) %>% 
    rename(Position2 = Parameters,
         beta2 = value) %>% 
  add_row(Position2 = "wearing_positionChest pin", beta2 = 0, .before = 1)

#third, collect all the beta coefficients for the interaction
coefs_extra <- 
  Model$beta %>% 
  as_tibble(rownames = "Parameters") %>% 
  filter(str_detect(Parameters, "wearing_position")) %>% 
  rename(Position = Parameters,
         beta3 = value) %>% 
  add_row(Position = "contextpublic:wearing_positionChest pin", beta3 = 0, .before = 2) %>%
  add_row(Position = "contextexercise:wearing_positionChest pin", beta3 = 0, .before = 3) %>%
  add_row(Position = "contextwork:wearing_positionChest pin", beta3 = 0, .before = 4) %>%
  add_row(Position = "contextsocial:wearing_positionChest pin", beta3 = 0, .before = 5) %>%
  mutate(Position = 
           str_replace(
             Position, "^wearing_position", "contexthome:wearing_position")
         )

#combine the three tables to a single table and filter out non-relevant combinations
coefs_combined <- 
expand_grid(coefs_context, coefs_position, coefs_extra) %>% 
  filter(str_detect(Position, Context),
         str_detect(Position, Position2)) %>% 
  mutate(Context = str_remove(Context, "context"), 
         Position = str_remove(Position, "(.*):wearing_position"),
         beta3 = ifelse(str_detect(Context , "home"), 0, beta3))

coefs_combined <- 
  set_names(coefs_combined$beta1+coefs_combined$beta2 + coefs_combined$beta3, 
            paste(coefs_combined$Context, coefs_combined$Position, sep = ":"))

#create and save a table of the predicted rating
combined_pred <- 
pred(coefs_combined, Model$Theta, 
     levels = levels(data_long2$rating)
     ) %>% 
  as_tibble(rownames = "Parameters") %>%
  mutate(
         `Parameters` = str_replace(`Parameters`, "reference", "home:Chest pin")
  ) %>% 
  separate_wider_delim(Parameters, ":", names = c("Context", "Position")) %>% 
  pivot_longer(cols = -c(Context, Position), names_to = "Rating", values_to = "Probability") %>% 
  mutate(Rating = factor(Rating, levels = levels(data_long2$rating))) %>% 
  group_by(Context, Position) %>% 
  summarize(Probability = Rating[which.max(Probability)], .groups = "drop") %>% 
  pivot_wider(names_from = Position, values_from = Probability) %>% 
  arrange(factor(Context, levels = levels(data_long2$context))) %>% 
  select(Context, all_of(levels(data_long2$wearing_position))) %>% 
  gt() %>% 
  gt::tab_caption(md("*Likelihood of wear* rating prediction depending on **context** and **wearing position**")) %>% 
  gt::data_color(columns = -Context, ordered = TRUE,
                 palette = "viridis"
                 ) %>% 
  cols_width(everything() ~ px(100))

combined_pred
gtsave(combined_pred, "output/02_tables/table_4_context_position.png")


```


### Wearlikelihood public

#### Model selection

```{r, public selection}
parameter <- "wearlikelihoodrating_public"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The only parameter which is supported by the data is `Wearing Position`. `Sex`, its interaction with `Wearing Position`, and `Sample` are not supported by the data. The resulting model `m5` is used for the following analysis.

#### Significant differences

```{r, public differences}
#final model
chosen_model <- "m5"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])



#Significance matrix
sig_matrix <- data_significance_matrix(Model)

P2 <- Significance_matrix(sig_matrix)

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P2, width = 4, height = 4.7)

P2

```

#### Predicted probabilities

```{r, public predictions}
#if one wanted to print predictions for different subject percentiles
stDev <-  as.numeric(attr(VarCorr(Model)$record_id, "stddev"))^2
# 5th percentile:
prob_table(Model$beta * qnorm(0.05) * stDev, 
           "Predicted probabilities for the **5th percentile** for **{parameter}**")
#average:
prob_table(Model$beta, 
           "Predicted probabilities for the **average person** for **{parameter}**")
# 95th percentile:
prob_table(Model$beta * qnorm(0.95) * stDev, 
           "Predicted probabilities for the **95th percentile** for **{parameter}**")

```

#### Model diagnostics

```{r, public diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
for(i in 1:145) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Wearlikelihood work

#### Model selection

```{r, work selection}
parameter <- "wearlikelihoodrating_work"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The only parameter which is supported by the data is `Wearing Position`. `Sex`, its interaction with `Wearing Position`, and `Sample` are not supported by the data. The resulting model `m5` is used for the following analysis.

#### Significant differences

```{r, work differences}
#final model
chosen_model <- "m5"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])

#Significance matrix
sig_matrix <- data_significance_matrix(Model)

P3 <- Significance_matrix(sig_matrix)

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P3, width = 4, height = 4.7)

P3

```

#### Predicted probabilities

```{r, work predictions}
#if one wanted to print predictions for different subject percentiles
stDev <-  as.numeric(attr(VarCorr(Model)$record_id, "stddev"))^2
# 5th percentile:
prob_table(Model$beta * qnorm(0.05) * stDev, 
           "Predicted probabilities for the **5th percentile** for **{parameter}**")
#average:
prob_table(Model$beta, 
           "Predicted probabilities for the **average person** for **{parameter}**")
# 95th percentile:
prob_table(Model$beta * qnorm(0.95) * stDev, 
           "Predicted probabilities for the **95th percentile** for **{parameter}**")

```

#### Model diagnostics

```{r, work diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
for(i in 1:145) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Wearlikelihood home

#### Model selection

```{r, home selection}
parameter <- "wearlikelihoodrating_home"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The only parameter which is supported by the data is `Wearing Position`. `Sex`, its interaction with `Wearing Position`, and `Sample` are not supported by the data. The resulting model `m5` is used for the following analysis.

#### Significant differences

```{r, home differences}
#final model
chosen_model <- "m5"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])

#Significance matrix
sig_matrix <- data_significance_matrix(Model)

P4 <- Significance_matrix(sig_matrix)

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P4, width = 4, height = 4.7)

P4

```

#### Predicted probabilities

```{r, home predictions}
#if one wanted to print predictions for different subject percentiles
stDev <-  as.numeric(attr(VarCorr(Model)$record_id, "stddev"))^2
# 5th percentile:
prob_table(Model$beta * qnorm(0.05) * stDev, 
           "Predicted probabilities for the **5th percentile** for **{parameter}**")
#average:
prob_table(Model$beta, 
           "Predicted probabilities for the **average person** for **{parameter}**")
# 95th percentile:
prob_table(Model$beta * qnorm(0.95) * stDev, 
           "Predicted probabilities for the **95th percentile** for **{parameter}**")

```

#### Model diagnostics

```{r, home diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
for(i in 1:145) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Wearlikelihood social

#### Model selection

```{r, social selection}
parameter <- "wearlikelihoodrating_social"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The data supports `Wearing Position`, and its interaction with `Sex`. `Sample` is not supported by the data. The resulting model `m4` is used for the following analysis.

#### Significant differences

```{r, social differences}
#final model
chosen_model <- "m4"
Model <- Models$model[Models$name == chosen_model][[1]]

summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])

#Significance matrix
sig_matrix <- data_significance_matrix(Model, subset = "true")
sig_matrix <- 
  sig_matrix %>% mutate(term = str_remove(term, "demographics_sex"))


P5 <- 
  Significance_matrix(
sig_matrix %>% filter(!str_detect(term, "Male")), sex = TRUE
) +
geom_tile(
data = sig_matrix %>% filter(str_detect(term,"Male") & different) %>% 
        mutate(term = str_remove(term, ":Male")), 
fill = "red")

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P5, width = 4, height = 4.7)

P5 

```

#### Model diagnostics

```{r, social diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:144, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:144, labels=ord.re)
axis(2)
for(i in 1:144) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:144, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:144, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Wearlikelihood exercise

#### Model selection

```{r, exercise selection}
parameter <- "wearlikelihoodrating_exercise"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The only parameter which is supported by the data is `Wearing Position`. `Sex`, its interaction with `Wearing Position`, and `Sample` are not supported by the data. The resulting model `m5` is used for the following analysis.

#### Significant differences

```{r, exercise differences}
#final model
chosen_model <- "m5"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])

#Significance matrix
sig_matrix <- data_significance_matrix(Model)

P6 <- Significance_matrix(sig_matrix)

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P6, width = 4, height = 4.7)

P6

```

#### Predicted probabilities

```{r, exercise predictions}
#if one wanted to print predictions for different subject percentiles
stDev <-  as.numeric(attr(VarCorr(Model)$record_id, "stddev"))^2
# 5th percentile:
prob_table(Model$beta * qnorm(0.05) * stDev, 
           "Predicted probabilities for the **5th percentile** for **{parameter}**")
#average:
prob_table(Model$beta, 
           "Predicted probabilities for the **average person** for **{parameter}**")
# 95th percentile:
prob_table(Model$beta * qnorm(0.95) * stDev, 
           "Predicted probabilities for the **95th percentile** for **{parameter}**")

```

#### Model diagnostics

```{r, exercise diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
for(i in 1:145) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Wear duration

#### Model selection

```{r, duration selection}
parameter <- "wearduration"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The data supports `Wearing Position`, and its interaction with `Sex`. `Sample` is not supported by the data. The resulting model `m4` is used for the following analysis.

#### Significant differences

```{r, duration differences}
#final model
chosen_model <- "m4"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])

#Significance matrix
sig_matrix <- data_significance_matrix(Model, subset = "true")
sig_matrix <- 
  sig_matrix %>% mutate(term = str_remove(term, "demographics_sex"))


P7 <- 
  Significance_matrix(
sig_matrix %>% filter(!str_detect(term, "Male")), sex = TRUE
) +
geom_tile(
data = sig_matrix %>% filter(str_detect(term,"Male") & different) %>% 
        mutate(term = str_remove(term, ":Male")), 
fill = "red")


ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P7, width = 4, height = 4.7)

P7

```

#### Model diagnostics

```{r, duration diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:144, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:144, labels=ord.re)
axis(2)
for(i in 1:144) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:144, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:144, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```

### Restriction

#### Model selection

```{r, restrict selection}
parameter <- "restrict"
parameter_symbol <- sym(parameter)

#model generation
Models <- Infe(!!parameter_symbol, data_long)

#model comparisons
Model_Comparisons(Models) %>% 
  gt(caption = md(glue("Model comparisons for **{parameter}**"))) %>% 
  fmt_number(decimals = 3)

```

The only parameter which is supported by the data is `Wearing Position`. `Sex`, its interaction with `Wearing Position`, and `Sample` are not supported by the data. The resulting model `m5` is used for the following analysis.

#### Significant differences

```{r, restrict differences}
#final model
chosen_model <- "m5"
Model <- Models$model[Models$name == chosen_model][[1]]
summary(Model)
#McFadden
McFadden(Model, Models$model[[6]])

#Significance matrix
sig_matrix <- data_significance_matrix(Model)

P8 <- Significance_matrix(sig_matrix)

ggsave(glue("output/04_unused/significance_matrix_{parameter}.pdf"), 
       P8, width = 4, height = 4.7)

P8

```

#### Predicted probabilities

```{r, restrict predictions}
#if one wanted to print predictions for different subject percentiles
stDev <-  as.numeric(attr(VarCorr(Model)$record_id, "stddev"))^2
# 5th percentile:
prob_table(Model$beta * qnorm(0.05) * stDev, 
           "Predicted probabilities for the **5th percentile** for **{parameter}**")
#average:
prob_table(Model$beta, 
           "Predicted probabilities for the **average person** for **{parameter}**")
# 95th percentile:
prob_table(Model$beta * qnorm(0.95) * stDev, 
           "Predicted probabilities for the **95th percentile** for **{parameter}**")

```

#### Model diagnostics

```{r, restrict diagnostics}
#random effect distribution with random effects
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
for(i in 1:145) segments(i, ci[i,1], i, ci[i,2])
abline(h=0, lty=2)

#without confidence intervals
ci <- Model$ranef+qnorm(0.975)*sqrt(Model$condVar) %o% c(-1,1)
ord.re <- order(Model$ranef)
ci <- ci[order(Model$ranef),]
plot(1:145, Model$ranef[ord.re], axes=FALSE, ylim=range(ci), xlab="Subject", ylab="Subject difference")
axis(1, at=1:145, labels=ord.re)
axis(2)
abline(h=0, lty=2)

```
:::

## Summary Graph

```{r}
a <- theme(plot.margin = margin(5, 10,5,5,"pt"))
b <- theme(plot.margin = margin(5, 5,5,10,"pt"))

(P1 + a + P2 + b) / (P3 + a + P4 + b) / (P5 + a + P6 + b) / (P7 + a + P8 + b) + 
  plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 20))

ggsave("output/01_figures/summary_graph_differences.pdf", width = 10, height = 20)

```
